The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Tr\"aff and Francesco Versaci, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-03-01 article/article.tex
asymptotic notations are more beautiful now

\section{Asymptotic notations}
\label{sec:asymptotic}
We use the following definitions for the asymptotic notations $O()$, $o()$ and $\Theta()$.

\begin{align*}
f(n) \in o(g(n)) &\Leftrightarrow \forall \epsilon > 0 \exists n_o\forall n> n_0: |f(n)|\leq \epsilon  |g(n)|\\
f(n) \in O(g(n)) &\Leftrightarrow \exists c > 0 \exists n_o\forall n> n_0: |f(n)|\leq c  |g(n)|\\
f(n) \in \Omega(g(n)) &\Leftrightarrow \exists c > 0 \exists n_o\forall n> n_0: c  |g(n)| \leq |f(n)| \\
f(n) \in \Theta(g(n)) &\Leftrightarrow f(n) \in \Omega(g(n)) \land f(n)\in O(g(n))
\end{align*}

@@

%bibliography
\bibliographystyle{acm}
\bibliography{sources} 
\end{document}

>>>>

\section{Asymptotic notations}
\label{sec:asymptotic}
We use the following definitions for the asymptotic notations \cite{CLRS01}, where $f(\cdot)$ and $g(\cdot)$ are positive functions with one argument $n\in \mathbb{N}$ and $n_0 \in \mathbb{N}$, $c \in \mathbb{R}_{\geq 0}$ are suitable constants.

\begin{align*}
f(n) \in O(g(n)) &\Leftrightarrow \exists c, n_0 \;\forall n> n_0: f(n)\leq c  g(n) \\
f(n) \in \Omega(g(n)) &\Leftrightarrow \exists c, n_0\;\forall n> n_0: cg(n) \leq f(n) \\
f(n) \in \Theta(g(n)) &\Leftrightarrow f(n) \in \Omega(g(n)) \land f(n)\in O(g(n)) \\
f(n) \in o(g(n)) &\Leftrightarrow \forall c \; \exists n_0\;\forall n> n_0: f(n) < cg(n)
\end{align*}

@@

%bibliography
\bibliographystyle{acm}
\bibliography{../sources} 
\end{document}
